Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-01 thesis/results.tex
Adding some more content to the results section, adding a bit more of a description to the results. Remove redundant question.

The classification results are tabulated below. The best performing algorithm
random forest was able to classify HTTP over Tor with 93.7\% accuracy and a
false positive rate of 3.7\%. HTTPS over Tor was more easily identified with a
97.7\% accuracy and low false positive rate of 0.3\%.

The table includes the true positive and false positive rate rate of each algorithm and
include the area under the receiver operating characteristic (ROC) curve. The
ROC is a tool used for evaluating the usefulness and comparing different
matching algorithms and is often used to compare Internet traffic
classification techniques \parencite{citeulike:167557,Nguyen:2008p3837}.

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    Algorithm & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

  Yes, the classification algorithms trialled were all able to identify Tor traffic
  with reasonable accuracy.

@@

  Insert answer here.

  \item{Does Tor traffic have characteristics that make it distinguishable using
    machine learning techniques?}

  Insert answer here.

>>>>

Traffic classification algorithms are evaluated using a number of metrics, the
primary of these being the true positive rate sometimes known as the detection
rate (DR) and the false positive rate. A strong traffic classifier typically
has a high true positive rate and a low false positive rate. In table
\ref{table:results} the true positive rate indicates the percentage of
individual sessions correctly classified as the listed protocol. The false
positive rate indicates the percentage of sessions incorrectly labelled as the
listed protocol. Included with these is the area under the receiver operating
characteristic (ROC) curve. The ROC is a tool used for evaluating the
usefulness and comparing different matching algorithms and is often used to
compare Internet traffic classification techniques
\parencite{citeulike:167557,Nguyen:2008p3837}.

All of the algorithms chosen were able to successfully classify HTTPS and HTTP
over Tor traffic with accuracy in excess of 90\%, with the Adaboost algorithm
unable to classify HTTPS over Tor. The best performing algorithm random forest
was able to classify HTTP over Tor with 93.7\% accuracy and a false positive
rate of 3.7\%. HTTPS over Tor was more easily identified with a 97.7\% accuracy
and low false positive rate of 0.3\%.

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046 & 0.963\\
    HTTP over Tor & 0.906 & 0.04 & 0.94\\
    HTTPS over Tor & 0.955 & 0.01 & 0.972\\
    Weighted Avg. & 0.941 & 0.037 & 0.957\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

    Under the controlled conditions of the experiment demonstrated within this
    thesis, comparing a sample of simulated encrypted network traffic produced
    by a commonly used web browser versus the same traffic routed over a
    demonstration Tor network, all the techniques used were able to classify
    Tor traffic with a high level of accuracy.

@@
